---
title: 'Stats 250: Homework 2'
author: "Instructional Team"
date: "Spring/Summer 2022"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Homework assignments will typically contain a coding-based question that tests your R knowledge learned in lab. We will provide you with an R Markdown template which you will use to create code that generates some desired output. This "desired output" might be a numerical summary, a table, a plot, or even the result of a statistical test. 

Remember, *Stats 250 is not a programming class*. If you need help, circle back to the lab documents or reach out to an instructor (in office hours or via email) for help!   


### Animal Rescues

The animals data set contains information about the animal rescue incidents attended to by the London Fire Department. Run the code chunk below to read in the data set.

```{r readAnimals}
rescues <- read.csv("animals.csv")
```

You should now see a "Data" object called `rescues` when you look in the global environment pane of R Studio (top right).

Feel free to run the code chunk below to preview the data set.

```{r previewAnimals}
head(rescues)
```

Use the functions you learned in Lab 2 to complete the following tasks. 


***


### Part A

Using the variable `Animal`, make an *appropriate plot* that will allow you to determine which animal is most likely to be rescued by the London Fire Department. Be sure to include a proper title (which states the type of plot and the name of the variable plotted) - as well as appropriate axis labels. Hint: feel free to copy, paste, and alter code chunks from Lab 2. 

```{r AnimalPlot, error = T}
# Replace this comment with your code

```


***


### Uploading Images to Course.Work. 
Please do not copy and paste your plot above (it wil only lead to errors in Course.Work). Instead, choose one of the options below!

- **Option 1:** Right click on your plot and click "Save Image"

- **Option 2:** Take a screenshot of the plot (Mac users can hit "Command + Shift + 4" to select the portion of the screen to capture; Windows users can hit "Windows logo + Shift + S" to do the same).

After completing Option 1 or 2, head to Course.Work and upload your image. **Again, please do not simply copy and paste the image to Course.Work.** 


***


### Part B

Use the `table()` function to create a two-way frequency table of `Animal` and `RescueType`. Remember, you can include row and column totals by using the `addmargins()` function.   

```{r AnimalTable, error = T}
# Replace this comment with your code

```

Don't forget to upload a screenshot of your table as part of your response. See Option 2 from the "Uploading Images to Course.Work" section above.

